Vertical and oblique transmission fluctuating in time and in space

### 2018-07-02 ms/ms_sunnyvale.tex
c->tau because c is already used for poly coef

Following migration~\citep{Karlin1981}, the frequencies of $A$ in the two demes are
\begin{equation} \label{eq:migration_model_migration}
\begin{aligned}
\gamma_1 x_1' &= (1-m) x_1^s + c m x_2^s, \quad \gamma_1 = (1-m) + c m, \\
\gamma_2 x_2' &= m x_1^s + c (1-m) x_2^s, \quad \gamma_2 = m + c (1-m),
\end{aligned}
\end{equation}
where $0 \le m \le 1/2$ is the migration rate, i.e. the fraction of the population that is replaced by migrants; $c>0$ is the relative size of deme 2 compared to deme 1 (at least where migration is concerned); and $\gamma_j$ is a normalizing factor.
This is a \emph{two-deme stepping-stone migration scheme}~\citep[][eqs.~2.15-16]{Karlin1982}.

@@

In the case of symmetric migration $c=1$ occurring after symmetric selection $w_1=1/w_2=w>1$, the recursions~\eqref{eq:migration_model_selection_transmission}~and~\eqref{eq:migration_model_migration} become
\begin{equation}\begin{aligned} \label{eq:migration_model_unconditional_symmetric}
x_1' &= (1-m)x_1\Big(\rho_1 \frac{w}{\overline w_1} + 1-\rho_1 \Big) + m x_2\Big(\rho_2 \frac{1/w}{\overline w_2} + 1-\rho_2 \Big), \\
x_2' &= m x_1\Big(\rho_1 \frac{w}{\overline w_1} + 1-\rho_1 \Big) + (1-m) x_2\Big(\rho_2 \frac{1/w}{\overline w_2} + 1-\rho_2 \Big).
\end{aligned}
\end{equation}
This is the \emph{homogeneous stepping-stone migration scheme}~\citep[][eq.~2.14]{Karlin1982}.

>>>>

Following migration~\citep{Karlin1981}, the frequencies of $A$ in the two demes are
\begin{equation} \label{eq:migration_model_migration}
\begin{aligned}
\gamma_1 x_1' &= (1-m) x_1^s + \tau m x_2^s, \quad \gamma_1 = (1-m) + \tau m, \\
\gamma_2 x_2' &= m x_1^s + \tau (1-m) x_2^s, \quad \gamma_2 = m + \tau (1-m),
\end{aligned}
\end{equation}
where $0 \le m \le 1/2$ is the migration rate, i.e. the fraction of the population that is replaced by migrants; $\tau>0$ is the relative size of deme 2 compared to deme 1 (at least where migration is concerned); and $\gamma_j$ is a normalizing factor.
This is a \emph{two-deme stepping-stone migration scheme}~\citep[][eqs.~2.15-16]{Karlin1982}.

@@

In the case of symmetric migration $\tau=1$ occurring after symmetric selection $w_1=1/w_2=w>1$, the recursions~\eqref{eq:migration_model_selection_transmission}~and~\eqref{eq:migration_model_migration} become
\begin{equation}\begin{aligned} \label{eq:migration_model_unconditional_symmetric}
x_1' &= (1-m)x_1\Big(\rho_1 \frac{w}{\overline w_1} + 1-\rho_1 \Big) + m x_2\Big(\rho_2 \frac{1/w}{\overline w_2} + 1-\rho_2 \Big), \\
x_2' &= m x_1\Big(\rho_1 \frac{w}{\overline w_1} + 1-\rho_1 \Big) + (1-m) x_2\Big(\rho_2 \frac{1/w}{\overline w_2} + 1-\rho_2 \Big).
\end{aligned}
\end{equation}
This is the \emph{homogeneous stepping-stone migration scheme}~\citep[][eq.~2.14]{Karlin1982}.
